##Abstract
This is a summary of exploratory analysis on three corpora of English-language text (US) from different online sources: blogs, news, and Twitter. 
[results]
##Introduction##
The study corpora are divided into three sources: blogs, news, and Twitter messages. For each corpora, we performed exploratory analysis to find the following metrics. 
file size
number of lines (empty and non-empty)
number of words
distribution of words, including most frequent words
number of characters (including and excluding spaces)

Analysis was performed using the ggplot2 and stringi packages in R. 

##Data
First, the data was loaded based on category. 

```{r eval=FALSE}
setwd("/Users/blair_stolk/Coursera-SwiftKey/final/en_US")
blogs <- readLines("./en_US.blogs.txt")
news <- readLines("./en_us.news.txt")
twitter <- readLines("./en_us.twitter.txt")
```
```{r eval=FALSE}
file.info(blogs)$size/1024^2
file.info(news)$size/1024^2
file.info(twitter)$size/1024
```

```{r}
library(stringi)
stri_stats_general(blogs)
stri_stats_general(news)
stri_stats_general(twitter)
```

```{r}
blogwords <- stri_count_words(blogs)
summary(blogwords)
qplot(blogwords)
```
```{r}
newswords <- stri_count_words(news)
summary(newswords)
qplot(newswords)
```

```{r}
twitwords <- stri_count_words(twitter)
summary(twitwords)
qplot(twitwords)
```
##Results##

The blog corpora was 200.42MB, and the news corpora similarly sized at 196.23MB. The Twitter corpora was somewhat smaller at 159.36MB. 
The blog corpora had  206,824,382 characters in total, 170,389,539
 excluding spaces, and 899,288 lines (none blank). The news corpora was of a similar size, with 203,223,154 characters (169,860866 excluding spaces) contained in 1,010242 lines with no blank lines found. 
The Twitter corpora also had no blank lines, but somewhat fewer characters (162,096,031 in total, 134,092,634 excluding spaces). 
The news and blog corpora show similar word frequency distributions. However, the Twitter corpora shows a frequency which is not log-normal, but this is likely a result of the character limit associated with Twitter. 
